\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{pdflscape}
\usepackage{arydshln}

\title{Hazard Analysis\\\progname}

\author{\authname}
\date{\today}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

~\newpage \pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}
\begin{table}[hp]
	\caption{Revision History} \label{TblRevisionHistory}
	\begin{tabularx}{\textwidth}{llX}
		\toprule
		\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
		\midrule
		October 17 & Jarrod Colwell & Created document structure\\
		October 17 & Talha Asif & Modifying Doc Structure\\
		October 17 & Talha Asif & Added introduction section content\\
		October 17 & Jarrod Colwell & Added scope and purpose section content\\
		October 19 & Andrew Carvalino & Definition of Hazard and Critical Assumptions\\
		October 19 & Talha Asif & Adding Section 8\\
		October 19 & Ali Tabar & Adding Sections 5 and 6\\
    October 19 & Madhi Nagarajan & Adding Sections 3 and 4\\
		\bottomrule
		\end{tabularx}
\end{table}

~\newpage \pagenumbering{arabic}

\section{Introduction}
Before going any further with system design, it is crucial to conduct a hazard analysis of the system from an engineering perspective. The goal is to identify critical safety concerns the application users could face and the solutions to them. Hazards will be determined using the Failure Modes and Effects Analysis (FMEA) for Flick Picker.

\section{Scope and Purpose}
This document covers the various areas in which the system is most vulnerable, including but not limited to:
\begin{itemize}
	\item External Resource Integration Points
	\item Server Communication
	\item TODO: Add more here or delete
\end{itemize}
Along with identifying the vulnerable areas of the system, this document also covers the strategies, both elimination and mitigation, and new security requirements to reduce or eliminate the impact that these hazards have.

\section{Background}
Flick Picker is a web application that finds the most compatible movie, TV show, or Anime for a group of users. Users will have the ability to set preferences related to their favourite genre, actors, movies etc. Based on these preferences, the system will produce personalized movie/TV show recommendations for users. The application will then determine the most liked film within the group.

\section{System Boundary}
The list below identifies the the various components part of the system:
\begin{enumerate}
	\item Flick-Picker Application: This consists of 3 main components.
	\begin{enumerate}
	  \item Authentication: Verifies and logs the user into the system.
	  \item Profile Management: Stores and manages the user's profile, including their username, preferences, groups etc. Note that this data is stored
	  \item Recommendation System: Provides movie/TV show recommendations to users and groups.
	\end{enumerate}
	\item The user's Physical Device (Laptop or Phone)
	\item External Media APIs (OMDb, MyAnimeList etc.): Our application requires these APIs to collect movie and TV show records.
	\item Database: Storing user data on our database, through Firebase.
	\& Application Hosting \& Deployments The application will be hosted through Firebase. Builds and deployments will be managed by Jenkins/GitHub Workflow.
	\
\end{enumerate}

\noindent The system boundary includes the entire Flick-Picker Application, and application database. Note that user's device and media APIs are external elements, therefore not part of the system boundary. Firebase/Google maintains the uptime of our application and database since we utilize of their services. We also make use of Jenkins/GitHub Workflow for CI/CD of our application.



\section{Scope of Hazard Analysis}
This document will identify safety concerns and solutions that users may face via defining what a hazard is in this context, stating the critical assumptions that are being made by the system, providing a Failure Modes and Effects Analysis of the components of the system, outlining the safety requirements that are a byproduct of that analysis, and outlining a roadmap of when the hazard analysis may be consulted or further adjusted. In addition, proper background of the project will also be provided, along with the scope and purpose.

\section{Definition of Hazard}
A hazard, as defined by Nancy Leveson, is a property or condition in the system, that may cause some sort of loss when combined with an environmental condition.

\section{Critical Assumptions}
\begin{enumerate}
	\item System will not have direct access to users' hardware (ex. specific CPU registers)
	\item Files will not be downloaded onto the users' device without the explicit consent of the user (should that be a feature of the system)
	\item Users' private information will not be sold or intentionally disclosed to any third parties
\end{enumerate}

\begin{landscape}
\newpage
\section{Failure Modes and Effects Analysis}
Below are tables containing the full Failure Modes and Effects Analysis.
\begin{table}[hp]
	\caption{Failure Modes and Effects 1} \label{TblFMEA1}
	\begin{tabularx}{\linewidth}{| p{0.2\textwidth} | X X p{0.25\textwidth} X l |}
		\hline
		Component & Failure Modes & Effects of Failure & Causes of Failure & Recommended Actions & SR \\
		\hline
		Database & Data is deleted on accident & All user data is lost & Database Failure & Regular backups exist where data can be rolled back on demand & IR2, IR3 \\
		\hdashline
		~ & Data is unavailable & User cannot access data & Database Failure & Refer Above & IR7 \\
		\hdashline
		~ & Data is modified incorrectly & User data is not updated & Database Failure & System alerts if data is not modified when requested & IR2 \\
		\hline
		Authentication & User cannot login & User cannot view recommendations or friends & Invalid Credentials & Use the correct credentials & AR1, PR1 \\
		\hline
		\end{tabularx}
\end{table}
\newpage
\begin{table}[hp]
	\caption{Failure Modes and Effects 2} \label{TblFMEA2}
	\begin{tabularx}{\linewidth}{| p{0.2\textwidth} | X X p{0.25\textwidth} X l |}
		\hline
		Component & Failure Modes & Effects of Failure & Causes of Failure & Recommended Actions & SR \\
		\hline
		Authentication & Impersonated Superadmin manipulates user's database & User data is changed on back-end, or deleted & Database Security Failure & Reset superadmin password and rollback database & AR2 \\
		\hline
		Show Selection & Show selection misses preferences & Group will be given a recommendation which does not match all preferences & Algorithmic Error & Group has to try a new recommendation or modify their preferences as none would match & PR2 \\
		\hdashline
		~ & Show selection takes too long & Group is given recommendations too slowly & Algorithmic Error & Server must be able to handle influx of requests at busy times & PR2 \\
		\hline
		\end{tabularx}
\end{table}
\newpage
\begin{table}[hp]
	\caption{Failure Modes and Effects 3} \label{TblFMEA3}
	\begin{tabularx}{\linewidth}{| p{0.17\textwidth} | X X p{0.25\textwidth} X l |}
		\hline
		Component & Failure Modes & Effects of Failure & Causes of Failure & Recommended Actions & SR \\
		\hline
		Browser & Application Crashes & Unsaved user data can be lost & General browser crash & Reopen browser application and fill in any data that was not saved & IR6 \\
		\hline
		Github Automation & Pipeline Not Automatically Run & The current build of will look like it has no issues but the tests were not run & GitHub Error & Manually start pipeline & IR4, IR5 \\
		\hline
		\end{tabularx}
\end{table}
\end{landscape}

\section{Safety Requirements}
Below are the Requirements that have been formed by the above analysis.

\subsection{Access Requirements}
\begin{itemize}
	\item AR1: Users can only access and modify their own data
	\item AR2: Only a superadmin can modify the database directly, which there is only one of
\end{itemize}

\subsection{Integrity Requirements}
\begin{itemize}
	\item IR1: User data is not modified without their permission
	\item IR2: Database backups occur daily
	\item IR3: Database backups are kept for at minimum one month
	\item IR4: CI/CD Pipeline is run before every deployment to ensure a healthy application state
	\item IR5: CI/CD Pipeline is run on every new code change before it can be merged
	\item IR6: Application crashes will not cause the device to stop working
	\item IR7: Database will be available as long as the service is available
\end{itemize}

\subsection{Privacy Requirements}
\begin{itemize}
	\item PR1: Users have to login with their credentials to access application data
	\item PR2: Algorithm to choose shows shall be protected
\end{itemize}

\subsection{Audit Requirements}
\begin{itemize}
	\item AT1: Requirements shall be easy to read and verify across the system
\end{itemize}

\section{Roadmap}
The safety requirements determined within this document will be considered throughout the development of the project. After completion of key components (Frontend, Backend, Database etc.), hazard analysis will be conducted to ensure that potential risks are mitigated. If any issues or risks are discovered, action will be taken immediately to resolve them.


\end{document}